---
title: "gatekeepR: a reviewable marker gating workflow"
author: "R. Heller"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{gatekeepR: a reviewable marker gating workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(gatekeepR)
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = TRUE)
```

`gatekeepR` turns per-cell marker measurements into reviewable phenotype and
state calls. The same prepared objects and classifier are used by batch code,
the review application, and the locked export. This keeps a reviewed result
replayable after the interactive session has ended.

## The complete workflow

The following code is the smallest end-to-end template. It uses a configuration
and a panel declared as data, then carries the result through correction,
thresholding, classification, state calls, structures, review, and export.

```{r workflow, eval=FALSE}
cfg <- gk_example_config()
prep <- gk_prepare(cells, config = cfg)
corrected <- gk_correct(prep, method = "robust_z")
thresholds <- gk_thresholds(prep, cfg, correction = corrected)
classification <- gk_classify(corrected, thresholds, config = cfg)
states <- gk_state_calls(corrected, thresholds, config = cfg)
structures <- gk_structures(classification, corrected)
review <- gk_review(classification, states, structures, thresholds, corrected)
reviewed <- gk_replay(review)

snapshot <- gk_lock(review, reviewer = "reviewer-01")
gk_export(snapshot, dir = "export")
gk_verify_export("export")
```

`gk_replay()` is the review boundary: it applies the append-only ledgers to
the initial calls and returns the effective reviewed state. `gk_save_review()`
and `gk_load_review()` persist the review package before export when work must
be resumed later.

## Outputs and auditability

The `classification`, `states`, and `structures` objects retain the cell and
image identifiers needed to join results back to source data. A locked export
contains the effective calls, review ledgers, configuration, provenance, and a
manifest. `gk_verify_export()` checks the manifest and replays the exported
decisions, so downstream code can reject incomplete or contradictory exports.

## Optional interfaces

Plots are thin views over the same objects used by batch code:

```{r plots, eval=FALSE}
gk_plot_map(reviewed, image_id = "image-01")
gk_plot_thresholds(thresholds)
gk_plot_overview(reviewed, image_id = "image-01")
```

The Shiny shell can load a review or an exported result with
`gk_app(review = review)` or `gk_app(export = export)`. The app does not create
a separate classification implementation.
