---
title: "Review and reproducibility"
author: "R. Heller"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Review and reproducibility}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(gatekeepR)
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

Review actions are append-only. Each action has an order, reviewer, reason,
and target identity. The effective result is calculated by replaying those
actions in order.

```{r review-template, eval=FALSE}
review <- gk_review(classification, states, structures, thresholds, prep)
review <- gk_set_cut(review, marker = "marker_a", estimate = 0.5,
  reviewer = "reviewer-01", reason = "manual boundary")
review <- gk_dispose(review, cell_id = "cell-001", disposition = "DELETE",
  reviewer = "reviewer-01", reason = "out of tissue")
reviewed <- gk_replay(review)
```

`gk_save_review()` writes a staged, checksummed review directory and
`gk_load_review()` restores it. Once the review is complete, `gk_lock()` blocks
further mutation and `gk_export()` writes the reproducible result. Verify it
before delivery:

```{r export-template, eval=FALSE}
gk_save_review(review, "review")
gk_lock(review, reviewer = "reviewer-01")
export <- gk_export(review, "export")
gk_verify_export(export)
```

The verification step checks identifiers, configuration and source hashes,
ledger replay, deletion history, and threshold hashes. It is suitable for a
batch validation job as well as for a human review handoff.
