---
title: "Threshold methods and callability"
author: "R. Heller"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Threshold methods and callability}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(gatekeepR)
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

Thresholds are estimates with evidence and status, not magic constants. List
the available methods with:

```{r methods}
gk_threshold_methods()
```

The density valley, density tail, Gaussian mixture, embedding crossing, and
parent-specific crossing methods can be selected in a batch run. A method may
return an explicit insufficient-support or non-finite status; callers should
inspect status and callability before treating a marker as usable.

```{r threshold-run, eval=FALSE}
thresholds <- gk_thresholds(
  corrected,
  method = "density_valley",
  marker = "marker_a"
)
gk_callability(thresholds)
gk_plot_thresholds(thresholds)
```

Manual corrections can replace an estimate through the review ledger. The
original estimate remains in the ledger, allowing the final result to explain
which cut was used and why.
